MCC Models

### 2019-09-03 papers/full_paper/models.Rmd
migrate manuscript and complete SI

@@

>>>>

```{r}
# preparing datafiles (delete eventually)

# d <- read_csv(file="../../stats/data/inf.data.csv") %>%
#   mutate(trial_type = ifelse(trial == "train", "train", "test"),
#          trial = alltrial -2,
#          experiment = "adult_ex1",
#          condition = ifelse(control == TRUE, "control", "test") )%>%
#   filter(trial_type == "test")%>%
#   select(experiment, id,  trial,condition, agent, correct)
# 
# write_csv(d , path="../../stats/data/adult_ex1.csv")
# 
# d <- read_csv(file="../../stats/data/novel.data.csv") %>%
#   mutate(trial_type = ifelse(trial == "train", "train", "test"),
#          experiment = "adult_ex2_novelty",
#          speaker = ifelse(change == TRUE, "different_speaker" , "same_speaker"),
#          agent = ifelse( condition == "same_speaker", agent, altAgent))%>%
#   filter(trial != "train")%>%
#   select(experiment, id, trial,speaker, agent, correct)
# 
# write_csv(d , path="../../stats/data/adult_ex2_novelty.csv")
# 
# d <- read_csv(file="../../stats/data/pref.data.csv") %>%
#   mutate(trial_type = ifelse(trial == "train", "train", "test"),
#          experiment = "adult_ex2_preference",
#          speaker = ifelse(change == TRUE, "different_speaker" , "same_speaker"),
#          agent = ifelse( condition == "same_speaker", agent, altAgent))%>%
#   filter(trial != "train")%>%
#   select(experiment, id, trial,speaker, agent, correct)
# 
# write_csv(d , path="../../stats/data/adult_ex2_preference.csv")
# 
# d <- bind_rows(read_csv(file="../../stats/data/ex3.novel.data.csv"),
#                read_csv(file="../../stats/data/ex3.pref.data.csv")) %>%
#   distinct(id, alltrial, .keep_all = TRUE) %>%
#   mutate(trial_type = ifelse(trial == "train1" | trial =="train2", "train", "test"))
# 
# exclude <- d %>%
#   filter(trial_type == "train") %>%
#   group_by(id)%>%
#   summarise(correct_inf = mean(correct_inf)) %>%
#   filter(correct_inf == 0)
# 
# d <- d%>%
#   filter(!id %in% exclude$id)%>%
#   mutate(agent = ifelse( change == "same", agent, altAgent),
#          common_ground_manipulation = ifelse(experiment == "novel_inf","novelty", "preference"),
#          experiment = "adult_ex3",
#          trial = alltrial -2,
#          speaker = ifelse(change == "same", "same_speaker", "different_speaker"))%>%
#   filter(trial_type == "test")%>%
#   select(experiment, id,trial, common_ground_manipulation, speaker ,alignment, agent, correct_inf)
# 
# write_csv(d , path="../../stats/data/adult_ex3.csv")
# 
# 
#
# d <- bind_rows(read_csv(file="../../stats/data/ex3.2.novel.strong.data.csv"),
#                read_csv(file="../../stats/data/ex3.2.novel.medium.data.csv"),
#                read_csv(file="../../stats/data/ex3.2.novel.weak.data.csv"),
#                read_csv(file="../../stats/data/ex3.2.pref.strong.data.csv"),
#                read_csv(file="../../stats/data/ex3.2.pref.medium.data.csv")
#                ) %>%
#   distinct(id, alltrial, .keep_all = TRUE) %>%
#   mutate(trial_type = ifelse(trial == "train1" | trial =="train2", "train", "test"))
#          
# exclude <- d %>%
#   filter(trial_type == "train") %>%
#   group_by(id)%>%
#   summarise(correct_inf = mean(correct_inf)) %>%
#   filter(correct_inf == 0)
# 
# d <- d%>%
#   filter(!id %in% exclude$id)%>%
#   mutate(agent = ifelse( change == "same", agent, altAgent),
#          common_ground_manipulation = ifelse(grepl("novel",experiment),"novelty", "preference"),
#          trial = alltrial -2,
#          speaker = ifelse(change == "same", "same_speaker", "different_speaker"),
#          prior_manipulation = prior,
#          experiment = "adult_ex4")%>%
#   filter(trial_type == "test")%>%
#   select(experiment, id,trial, common_ground_manipulation, prior_manipulation, speaker, alignment, agent, correct_inf)
# 
# write_csv(d , path="../../stats/data/adult_ex4.csv")
#
# 
# d <- bind_rows(read_csv(file="../../stats/data/kids_pref_data.csv")%>%filter(age != "2")%>%mutate(speakerChange = change),
#                        read_csv(file="../../stats/data/kids_pref_2_data.csv")%>% mutate(age = subage))%>%
#   filter(trial != "train")%>%
#   mutate(age_bin = factor(age),
#          experiment = "child_ex2",
#          condition = ifelse(speakerChange == F, "same_speaker", "different_speaker"),
#          agent = ifelse( speakerChange == F, agent, altAgent),
#          id = subid,
#          minage = min(age_num))%>%
#   filter(trial != "train")%>%
#   select(experiment,id,age_bin,age_num,minage,trial,condition,agent,correct)
# 
# write_csv(d , path="../../stats/data/child_ex2.csv")
# 
# d <- bind_rows(
#   read_csv(file="../../stats/data/kids_inf_data.csv"),
#   read_csv(file="../../stats/data/kids_inf_2_data.csv"))%>%
#   filter(subage != "2",
#          trial != "filler1",
#          trial != "filler2")%>%
#   mutate(age_bin = factor(subage),
#          experiment = "child_ex1",
#          id =subid,
#          minage = min(age_num))%>%
#   select(experiment,id,age_bin,age_num,sex,minage,trial,correct)
# 
# write_csv(d , path="../../stats/data/child_ex1.csv")
#
# d <- read_csv(file="../../stats/data/kids_ex3_data.csv")%>%
#   mutate(experiment = "child_ex3",
#          id = subid,
#          age_bin = subage,
#          speaker = Speaker,
#          alignment = Alignment,
#          minage = min(age_num))%>%
#   filter(trial != "filler1",trial != "filler2")%>%
#   select(experiment, id,age_bin,age_num,minage,trial, speaker, alignment, agent, correct_inf)
# 
#  write_csv(d , path="../../stats/data/child_ex3.csv")

@@

```{r ex4 prior pre-tests data adults}
# load data from prior strength manipulation experiments to set priors
adult_ex4_prior_data <-read_csv(file="../../stats/data/adult_ex4_prior.csv") 
```
